The Unicode Cookbook \linebreak for Linguists

### 2015-12-15 book/unicode.tex
adds preface

\include{chapters/introduction}
\include{chapters/pitfalls}
\include{chapters/ipa_meets_unicode}
\include{chapters/orthography_profiles}
\include{chapters/use_cases}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
echo 'this is a simple bash example'
echo 'this is a simple bash example'
ls | wc
## this is a simple bash example
## this is a simple bash example
##       10      10     165
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
"this is a simple R example"
## [1] "this is a simple R example"

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
library(qlcData)
example <- "AΑА"
profile <- write.profile(example)
\end{verbatim}
\end{kframe}
\end{knitrout}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Oct 19 18:08:51 2015
\begin{table}[H]
\centering
{\small
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
A & 1 & U+0041 & LATIN CAPITAL LETTER A \\ 
  Α & 1 & U+0391 & GREEK CAPITAL LETTER ALPHA \\ 
  А & 1 & U+0410 & CYRILLIC CAPITAL LETTER A \\ 
   \bottomrule
\end{tabular}
}
\caption{test} 
\label{bla}
\end{table}

You can refer to variables by using \textbackslash Sexpr{}. 
For example, the length of the example string is 3.
Crossreferencing also works, see Table~\ref{bla}.

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
print('bla' + 'bla')
print(3+4)
## blabla
## 7
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\include{chapters/preface}
\include{chapters/introduction}
\include{chapters/pitfalls}
\include{chapters/ipa_background}
\include{chapters/ipa_meets_unicode}
\include{chapters/orthography_profiles}
\include{chapters/use_cases}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
echo 'this is a simple bash example'
ls | wc
## this is a simple bash example
##       18      18     306
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## note that bash chunks are executed as one, with all output at the end.
## You will have to make different chunks to get output separated.
## And add manual linebreaks!
\end{verbatim}
\end{kframe}
\end{knitrout}

Spacing of lines is fine. I think without background looks better

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
# adding comments inside code? Probably not a good idea
(example <- "this is a simple R example")
## [1] "this is a simple R example"

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
library(qlcData)
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in library(qlcData): there is no package called 'qlcData'}}\begin{verbatim}
profile <- write.profile("AΑА")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(expr, envir, enclos): could not find function "{}write.profile"{}}}\end{kframe}
\end{knitrout}

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(xtable(profile, caption = "{}test"{}, label = "{}bla"{}), include.rownames = FALSE, : could not find function "{}xtable"{}}}\end{kframe}

You can refer to variables by using \textbackslash Sexpr{}. 
For example, the length of the example string is 26.
Crossreferencing also works, see Table~\ref{bla}.

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
print('bla' + 'bla')
print(3+4)
## blabla
## 7
\end{verbatim}
\end{kframe}
\end{knitrout}
